---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
![Build packages](https://github.com/kvasilopoulos/drat/workflows/Build%20packages/badge.svg)

There are two ways to install packages from this [drat repo](https://github.com/kvasilopoulos/drat).

1. By specifying the repo in `install.packages()`

```r
install.packages('exuberdata', repos = 'https://kvasilopoulos.github.io/drat/', type = 'source')
```

2. By registering `kvasilopoulos` repository as a valid repository

```r
install.packages("drat")
drat:::add("kvasilopoulos")
```
Now you can install and update packages without specfying the `repo` and the `type`.

```r
install.packages("exuberdata")
```

# Maintaining this page

## drat.builder and gh-actions

Instructions on the how to set up drat.builder with gh-actions are in this [ Post](https://zkamvar.netlify.app/) by [Zhian N. Kamvar](https://github.com/zkamvar).

The packages included in this drat repository are maintained in the
[packages.txt], which contains the github accounts and names of
the packages.

The data and metadata associated with this page are built with the
[{drat.builder}](https://github.com/richfitz/drat.builder) package. 

## Automated builds

This page is maintained under a [GitHub Action] that will check if the packages
updated and build them to this repo. If you want to update a package (e.g.
change its version number), edit the [packages.txt] file and the [GitHub
Action] will update the packages automagically. 

## Manual builds

Assuming the above works just fine, you shouldn't have to use this, but it is
here for posterity.

Install {drat.builder} via {remotes}:

```r
remotes::install_github("richfitz/drat.builder")
```

Steps for updating this page:

1. Pull from the remote to make sure you have the entire history
2. Open R from this directory
3. Run `drat.builder::build()`
4. push the changes

[packages.txt]: ./packages.txt
[GitHub Action]: https://github.com/kvasilopoulos/drat/actions?query=workflow%3A%22Build+packages%22

## Content

```{r echo=FALSE}
list.files(pattern = "tar", "src/contrib/")
```

## More

You can learn more about drat from the vignettes Drat for Package Users and Drat for Package Authors.
